%-----------------------------------------------------------------------------
% Author: Rayla Kurosaki
% GitHub: https://github.com/rkp1503
%-----------------------------------------------------------------------------
\documentclass{rayla-project}
\usepackage{rayla-math-style}

%-----------------------------------------------------------------------------
% Project Information
%-----------------------------------------------------------------------------
\myUniversity{
    Rochester Institute of Technology\\
    College of Science\\
    School of Mathematical Sciences
    }
\myTitle{Bifurcation of Systems}
\myName{Ramsey (Rayla) Phuc}
\courseid{MATH-631.01}
\courseName{Dynamical Systems}
\professorName{Dr. Niels Otani}
\term{2021-2022 Fall}
\dueDate{December 9th, 2021}

%-----------------------------------------------------------------------------
% Start of Document
%-----------------------------------------------------------------------------
\begin{document}

    \maketitle

    %-------------------------------------------------------------------------
    % Abstract
    %-------------------------------------------------------------------------
    \begin{abstract}
        Bifurcation theory plays a fundamental role in understanding the qualitative behavior of dynamical systems. In this paper, we present a comprehensive study of various bifurcations within a carefully constructed system of equations. Our objective is to investigate the dynamic changes and transitions that occur as system parameters are varied. First, we establish a set of equations that capture the essential characteristics of the dynamical system under investigation. These equations are derived based on a thorough analysis of the underlying physical or mathematical phenomenon of interest. We ensure that the system exhibits nonlinear behavior and contains appropriate parameters to facilitate the exploration of bifurcations. Next, we employ analytical techniques to investigate the bifurcation points within the system. By analyzing the stability and eigenvalues of the system, we determine the types of bifurcations that arise, such as saddle-node, transcritical, pitchfork, and Hopf bifurcations. Furthermore, we utilize graphical tools, such as bifurcation diagrams and phase portraits, to visualize and interpret the bifurcation phenomena. In summary, this paper presents a systematic approach to construct a system of equations and investigates the bifurcations within it. Our findings contribute to the broader understanding of bifurcation theory and its applications, providing a valuable framework for exploring and analyzing the dynamic behavior of complex systems.
    \end{abstract}

    %-------------------------------------------------------------------------
    % Body
    %-------------------------------------------------------------------------
    \input{contents/introducing-the-system.tex}
    \input{contents/constructing-the-system.tex}
    \input{contents/jacobian-matrix.tex}
    \input{contents/fixed-point-analysis.tex}
    \input{contents/hopf-bifurcation-analysis.tex}
    \input{contents/pitchfork-bifurcation-analysis.tex}

    %-------------------------------------------------------------------------
    % Bibliography
    %-------------------------------------------------------------------------
    \newpage
    % \nocite{*}
    \printbibliography[title={Bibliography}]

    %-------------------------------------------------------------------------
    % Appendix
    %-------------------------------------------------------------------------
    \newpage
    \appendix
    \input{appendices/figures.tex}

\end{document}
